\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2013-12-15 paper/paper.tex
Mostly spelling fixes

A time-varying value of a polymorphic type \texttt{a} is represented by
\texttt{Signal a}. For example, the term \texttt{constant 150} has type
\texttt{Signal Int}. The combinator \texttt{constant} creates a signal
whose value never changes. A more interesting signal is the primitive
\texttt{Window.dimensions : Signal (Int, Int)}. This signal represents
the browser window size and updates whenever it is resized. Signals are
asynchronous in that they update at no set time, just as the window may
remain the same size idefinitely. Signals update in discrete events, but
are continuous in the sense that they are always defined.

@@

The signals in an Elm program can be thought of as a Directed Acyclic
Graph (DAG). Many signals depend on other signals for their output. For
example, the \texttt{area} signal depends on \texttt{Window.dimensions}
signal. Similarly, the \texttt{area2} signal depends on both the values
of the \texttt{Window.width} and the \texttt{Window.height} signals.
When an event is fired on a signal, it propogates down the DAG to all
signals who depend on that signal and the outputs of those signals are
reevaluated.

@@

Notice that \texttt{pool.hoverable} is partially applied to \texttt{id}
purely, and then lifted on to the argument. This is possible,
utlimately, because \texttt{pool.hoverable} is pure.

@@

It is not just hover detection that follows the convention of the two
names primitives, singular and plural, but most of Elm's wrappers around
HTML GUI components. They are therefore receptive of the same join
technique. For labelled buttons, press events are represented by unit or
a provided identifier:

@@

Drop-down menus do not use the same paradigm as the rest; there is
\texttt{dropDown} but no \texttt{dropDowns}. This is unfortunate not
only because there seems to be no way to supply a
\texttt{Signal {[}String{]}}, but because drop-downs are commonly used
in groups. Multiple menus reporting on one signal would be very
convenient. If the menus were dynamic, it may be useful to determine
when an event occurs because the user makes a selection vs.~when the
menu updates and the previously selected string is no longer available.

@@

Our second trick fixed a race condition. A submenu was rendered to the
screen if one of three conditions was met: the mouse was hovering upon
its parent, the mouse was hovering upon it, or the mouse was hovering
upon any of its descendents. As the mouse moved from the parent to the
child, the child was often replaced with a spacer before it could detect
that the mouse was hovering over it. To fix this problem, we created the
following function:

@@

TodoFRP presents the user with a text field asking, ``what needs to be
done?''. Entered todo entries become DOM elements, which can be deleted
with a ``x'' button, also a DOM element. The button is implemented using
the \texttt{Graphics.Input} function

@@

Notice the similarity with \texttt{hoverables}. Each call of
\texttt{customButton} provides the identifier event when the button is
clicked, and three (pure) Elements to display: one normally, one on
hover, and one on click. The result is an \texttt{Element}, not a
\texttt{Signal Element}, that nevertheless changes among those three in
response to the mouse. This is possible because the result Element's
dimensions are taken to be the maximum of the three inputs' dimensions.
Even if the Elements have different sizes, the resulting element and
therefore the hover surface remains fixed in size. Although the same
join technique can be applied, we find it likely that it would not work
as intended.

In the case of TodoFRP, these Elements are diferent colors of the ``x''
and the same for each todo entry. The polymorphic \texttt{a}s are unique
identifiers (ascending integers) for each entry.

The todo label Elements are dynamic and do not detect hover information.
The button Elements that do detect hover information are known
statically. Without \texttt{hoverablesJoin}, it would be impossible to
dismiss a todo by clicking on its text label.

@@

\subsection{References}\label{references}
\end{document}

>>>>

A time-varying value of a polymorphic type \texttt{a} is represented by
\texttt{Signal a}. For example, the term \texttt{constant 150} has type
\texttt{Signal Int}. The combinator \texttt{constant} creates a signal
whose value never changes. A more interesting signal is the primitive
\texttt{Window.dimensions : Signal (Int, Int)}. This signal represents
the browser window size and updates whenever it is resized. Signals are
asynchronous in that they update at no set time, just as the window may
remain the same size indefinitely. Signals update in discrete events, but
are continuous in the sense that they are always defined.

@@

The signals in an Elm program can be thought of as a Directed Acyclic
Graph (DAG). Many signals depend on other signals for their output. For
example, the \texttt{area} signal depends on \texttt{Window.dimensions}
signal. Similarly, the \texttt{area2} signal depends on both the values
of the \texttt{Window.width} and the \texttt{Window.height} signals.
When an event is fired on a signal, it propagates down the DAG to all
signals who depend on that signal and the outputs of those signals are
reevaluated.

@@

Notice that \texttt{pool.hoverable} is partially applied to \texttt{id}
purely, and then lifted on to the argument. This is possible,
ultimately, because \texttt{pool.hoverable} is pure.

@@

It is not just hover detection that follows the convention of the two
names primitives, singular and plural, but most of Elm's wrappers around
HTML GUI components. They are therefore receptive of the same join
technique. For labeled buttons, press events are represented by unit or
a provided identifier:

@@

Drop-down menus do not use the same paradigm as the rest; there is
\texttt{dropDown} but no \texttt{dropDowns}. This is unfortunate not
only because there seems to be no way to supply a
\texttt{Signal {[}String{]}}, but because drop-downs are commonly used
in groups. Multiple menus reporting on one signal would be very
convenient. If the menus were dynamic, it would be useful to determine
when an event occurred because the user makes a selection vs.~when the
menu updated and the previously selected string was no longer available.

@@

Our second trick fixed a race condition. A submenu was rendered to the
screen if one of three conditions was met: the mouse was hovering upon
its parent, the mouse was hovering upon it, or the mouse was hovering
upon any of its descendants. As the mouse moved from the parent to the
child, the child was often replaced with a spacer before it could detect
that the mouse was hovering over it. To fix this problem, we created the
following function:

@@

TodoFRP presents the user with a text field asking, ``what needs to be
done?''. Entered TODO entries become DOM elements, which can be deleted
with a ``x'' button, also a DOM element. The button is implemented using
the \texttt{Graphics.Input} function

@@

Notice the similarity with \texttt{hoverables}. Each call of
\texttt{customButton} provides the identifier event when the button is
clicked, and three (pure) Elements to display: one normally, one on
hover, and one on click. The result is an \texttt{Element}, not a
\texttt{Signal Element}, that nevertheless changes among those three in
response to the mouse. This is possible because the result Element's
dimensions are taken to be the maximum of the three inputs' dimensions.
Even if the Elements have different sizes, the resulting element and
therefore the hover surface remains fixed in size. Although the same
join technique can be applied, we find it likely that it would not work
as intended.
%Note to Max: I think it does work...

In the case of TodoFRP, these Elements are different colors of the ``x''
and the same for each TODO entry. The polymorphic \texttt{a}s are unique
identifiers (ascending integers) for each entry.

The TODO label Elements are dynamic and do not detect hover information.
The button Elements that do detect hover information are known
statically. Without \texttt{hoverablesJoin}, it would be impossible to
dismiss a TODO by clicking on its text label.

@@

\subsection{References}\label{references}
%Make sure to put a link to our GitHub

\end{document}
